---
title: "README"
author: "Andrew Davis"
date: "`r Sys.Date()`"
output:
  github_document:
    toc: TRUE
---

## Overview

This directory contains an exploratory analysis of 

## Metadata:


## Input Data

The [](Input_data/a) was sent to me by ___ on //.


## Analysis pipeline:

1. 



## Output:

The remaining output files were saved to the "Results" and folder in this repository.

```{r, echo=FALSE}
list.files(path="Results")
```

## Required Libraries

These analyses were performed in RStudio 3.5.0 using (in alphabetical order):

* dplyr `r packageVersion("dplyr")`


All of the above are available from [CRAN](https://cran.r-project.org) or [Bioconductor](https://bioconductor.org/)

## Mechanics

The analysis in this project proceeds by running the Rmd files in R in numerical sequence

The Rmd scripts are as follows:

```{r, echo=FALSE}
list.files(path="R_scripts")
```


## Summary: 

## To do list:

1. Check genes for differential expression in the Uniderma ex vivo and clinical datasets.
2. Present findings to rest of team.

### Session information

```{r session_info}
sessionInfo()
```

This document was processed on: `r Sys.Date()`.




